Querying Integrated Scientific Observation and Measurement Data

### 2010-04-30 docs/algdraft/DataIntegration/DataIntegration.tex
Rerich query rewriting processing.

\section{Querying annotated and integrated ecological data}

@@

\subsection{Querying over Materialized database}\label{sec:matdb}

\subsubsection{Materialize data}

@@

\begin{example}
{\bf TODO: refine this example}
Take KQ1 as example. 
concept = observation, cond is {\em species = ``Picea rubens''};

From the annotation, find the {\em measurement type} with {\em
  Characteristic} species. 
Here, it is $m_3$. From the mapping, we find that the attribute in the
table is {\em spp}.

The second step is to find the data file which really have this
value. 
For this one, we find the data table, and do a select on the table
content.

Use materialized database: 
The first step is the same, after we know the data file, then we
search the table {\em measurement\_instance} with the {\em mvalue=``Picea rubens''}.

In this example, the computation cost is to search the different data
tables. To reduce this computation cost, we can materialize just the
measurement values. (How to do this? ) need more details.

Half materialized: how to perform query over it. 
\end{example}

>>>>

\section{Querying annotated and integrated OM data}

@@

@@

\begin{example}\label{eg:query_reqerite_q1}
Take $Q_1$ as example. The {\tt concept} is ``observation'' and {\tt cond} is {\em species = ``Picea rubens''};

From the annotation $A.MeasType$, we can find the measurement type
$m_3$ with the characteristic {\em species}. 
From the mapping $A.Map$, we further find that the attribute {\em spp} that the
measurement type $m_3$ is mapped to.

The second step is to find the data file which really have this value. 
For this one, we find the data table, and do a selection on the table content. 
\end{example}

From the above description, we can tell that the computation cost is to search the different data
tables. This way, for each candidate data table, we need to send an
SQL query to the server for evaluation purpose.
If the number of candidate data tables are small. This method should
work well. However, when we have a lot of candidate data tables, the
efficiency may be affected. 
In what follows, we introduce another strategy, which logically merge
the data content in different tables and perform queries ober the
materialized database.

\subsection{Querying over materialized database}\label{sec:matdb}

The previous section shows the method to rewrite a given query. 
In this section, we would discribe another strategy.

In this method, we merge the data in different tables into several
core OBOE tables, denoted by $OBOE.*$
In detail,
\begin{itemize}
\item $OBOE.EntityIns=\{\langle \underline{EntId}, EntType\rangle\}$ for all the entity instances;
\item $OBOE.ObsIns=\{\langle \underline{ObsId}, ObsType, EntId \rangle\}$ keeps all the observation instances;
\item $OBOE.MeasIns=\{\langle \underline{MeasId}, ObsId, MeasType, Val\rangle\}$ for all the measurement instances;
\item $OBOE.ContextIns =\{\langle \underline{ObsId, ConextObsId, ContextType}\rangle\}$ for all the context instances;
\end{itemize}

\subsubsection{Materialize data}
{\bf: TODO: refine the writing in MaterializeDB and move them here.}

\begin{example} \label{eg:materialize_db_q1}
Example \ref{eg:query_reqerite_q1} shows how to deal with $Q_1$ using
the query rewriting method. 
Using the  materialized database, the first step is the same.
After we know the data file, then we search the table {\em measurement\_instance} with the {\em mvalue=``Picea rubens''}. 
\end{example}
